\textbf{Supporting Information:}

### 2020-04-05 Supplementary_material/Supp_Material.Rmd
Changing font size and spacing
Preparing appendix to have an rmd file for chapter 1

---
title: "__Supporting Information:__"
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    toc: false
---

@@

>>>>

---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    toc: false
fontsize: 12pt
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage{float}

---

# Supporting information:

@@

\newpage

```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
library(knitr)
library(kableExtra)

Species <- c("Brassica oleracea", "Brassica rapa", "Eruca sativa", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")

Species <- as.character(Species)

Common_names <- c("Wild cabbage", "Pak choi", "Rocket", "White mustard", "Water spinach", "Morning glory", "Capsicum", "Petunia", "Tomato", "Eggplant")

Common_names <- as.character(Common_names)

Variety <- c("Capitata", "Chinensis", "", "", "", "", "California Wonder", "", "Tommy Toe", "Little Fingers")

Variety <- as.character(Variety)

Source <- c("https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.theseedcollection.com.au/", "http://www.shaman-australis.com.au", "https://www.edenseeds.com.au", "https://www.dianeseeds.com/", "https://www.mrfothergills.com.au/", "https://www.4seasonsseeds.com.au/")

Source <- as.character(Source)

t <- data.frame(Species, Common_names, Variety, Source)

kable(t, "latex", booktabs = T) %>%
kable_styling(font_size = 7)
```

### 2020-04-05 Supplementary_material/Supp_Material.tex
Changing font size and spacing
Preparing appendix to have an rmd file for chapter 1

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Supporting Information:},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\title{\textbf{Supporting Information:}}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

@@

Figure S7. Grouped effect sizes by family for each recipient species.

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{setspace}\doublespacing
\usepackage{float}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\section{Supporting information:}\label{supporting-information}

@@

\textbf{Figure S7.} Grouped effect sizes by family for each recipient
species.

\newpage

\begin{table}[H]
\centering\begingroup\fontsize{7}{9}\selectfont

\begin{tabular}{llll}
\toprule
Species & Common\_names & Variety & Source\\
\midrule
Brassica oleracea & Wild cabbage & Capitata & https://www.mrfothergills.com.au/\\
Brassica rapa & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
Eruca sativa & Rocket &  & https://www.mrfothergills.com.au/\\
Sinapis alba & White mustard &  & https://www.mrfothergills.com.au/\\
Ipomoea aquatica & Water spinach &  & https://www.theseedcollection.com.au/\\
\addlinespace
Ipomoea purpurea & Morning glory &  & http://www.shaman-australis.com.au\\
Capsicum annuum & Capsicum & California Wonder & https://www.edenseeds.com.au\\
Petunia integrifolia & Petunia &  & https://www.dianeseeds.com/\\
Solanum lycopersicum & Tomato & Tommy Toe & https://www.mrfothergills.com.au/\\
Solanum melongena & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}
